---
title: "Wastewater Surviellence for SARS-CoV-2 in Athens, GA"
author: "Lipp Laboratory, Department of Environmental Health Science, University of Georgia"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc_depth: 3
---
Load all required libraries.
```{r}
library(tidyverse)
library(plotly)
library(broom)
```

Read in raw data from RDS.
```{r}
raw_data <- readRDS("./n1_n2_cleaned_cases.rds")
```

Make a few small modifications to names and data for visualizations.
```{r}
final_data <- raw_data %>% mutate(log_copy_per_L = log10(mean_copy_num_L)) %>%
  rename(Facility = wrf) %>%
  mutate(Facility = recode(Facility, 
                           "NO" = "WRF A",
                           "MI" = "WRF B",
                           "CC" = "WRF C"))
```


Seperate the data by gene target to ease layering in the final plot
```{r}
#make three data layers
only_positives <<- subset(final_data, (!is.na(final_data$Facility)))
only_n1 <- subset(only_positives, target == "N1")
only_n2 <- subset(only_positives, target == "N2")
only_background <<-final_data %>% 
  select(c(date, cases_cum_clarke, new_cases_clarke, X7_day_ave_clarke, cases_per_100000_clarke)) %>%
  group_by(date) %>% summarise_if(is.numeric, mean)

#specify fun colors
background_color <- "#7570B3"
seven_day_ave_color <- "#E6AB02"
marker_colors <- c("N1" = '#1B9E77',"N2" ='#D95F02')
    
```

```{r}
#remove facilty C for now
#only_n1 <- only_n1[!(only_n1$Facility == "WRF C"),]
#only_n2 <- only_n2[!(only_n2$Facility == "WRF C"),]

only_n1 <- only_n1[!(only_n1$Facility == "WRF A" & only_n1$date == "2020-11-02"), ]
only_n2 <- only_n2[!(only_n2$Facility == "WRF A" & only_n2$date == "2020-11-02"), ]

```

Build the main plot
```{r}
#KEEP BOTH TARGETS HERE ON THE ALL DATA PLOT

      #first layer is the background epidemic curve
        p1 <- only_background %>%
              plotly::plot_ly() %>%
              plotly::add_trace(x = ~date, y = ~new_cases_clarke, 
                                type = "bar", 
                                hoverinfo = "text",
                                text = ~paste('</br> Date: ', date,
                                                     '</br> Daily Cases: ', new_cases_clarke),
                                alpha = 0.5,
                                name = "Daily Reported Cases",
                                color = background_color,
                                colors = background_color,
                                showlegend = FALSE) %>%
            layout(yaxis = list(title = "Daily Cases", showline=TRUE)) %>%
            layout(legend = list(orientation = "h", x = 0.2, y = -0.3))
        
        #renders the main plot layer two as seven day moving average
        p1 <- p1 %>% plotly::add_trace(x = ~date, y = ~X7_day_ave_clarke, 
                             type = "scatter",
                             mode = "lines",
                             hoverinfo = "text",
                            text = ~paste('</br> Date: ', date,
                                                     '</br> Seven-Day Moving Average: ', X7_day_ave_clarke),
                             name = "Seven Day Moving Average Athens",
                             line = list(color = seven_day_ave_color),
                             showlegend = FALSE)
      

        
        #renders the main plot layer three as positive target hits
        
        p2 <- plotly::plot_ly() %>%
          plotly::add_trace(x = ~date, y = ~mean_copy_num_L,
                                       type = "scatter",
                                       mode = "markers",
                                       hoverinfo = "text",
                                       text = ~paste('</br> Date: ', date,
                                                     '</br> Facility: ', Facility,
                                                     '</br> Target: ', target,
                                                     '</br> Copies/L: ', round(mean_copy_num_L, digits = 2)),
                                       data = only_n1,
                                       symbol = ~Facility,
                                       marker = list(color = '#1B9E77', size = 8, opacity = 0.65),
                                       showlegend = FALSE) %>%
          plotly::add_trace(x = ~date, y = ~mean_copy_num_L,
                                       type = "scatter",
                                       mode = "markers",
                                       hoverinfo = "text",
                                       text = ~paste('</br> Date: ', date,
                                                     '</br> Facility: ', Facility,
                                                     '</br> Target: ', target,
                                                     '</br> Copies/L: ', round(mean_copy_num_L, digits = 2)),
                                       data = only_n2,
                                       symbol = ~Facility,
                                       marker = list(color = '#D95F02', size = 8, opacity = 0.65),
                                       showlegend = FALSE) %>%
            layout(yaxis = list(title = "SARS CoV-2 Copies/L", 
                                 showline = TRUE,
                                 type = "log",
                                 dtick = 1,
                                 automargin = TRUE)) %>%
            layout(legend = list(orientation = "h", x = 0.2, y = -0.3))
        
        #adds the limit of detection dashed line
        p2 <- p2 %>% plotly::add_segments(x = as.Date("2020-03-14"), 
                                          xend = ~max(date + 10), 
                                          y = 3571.429, yend = 3571.429,
                                          opacity = 0.35,
                                          line = list(color = "black", dash = "dash")) %>%
          layout(annotations = list(x = as.Date("2020-03-28"), y = 3.8, xref = "x", yref = "y", 
                                    text = "Limit of Detection", showarrow = FALSE))

        

        p1
        p2
        
```
Combine the two main plot pieces as a subplot

```{r}
p_combined <-
    plotly::subplot(p2,p1, # plots to combine, top to bottom
      nrows = 2,
      heights = c(.6,.4),  # relative heights of the two plots
      shareX = TRUE,  # plots will share an X axis
      titleY = TRUE
    ) %>%
    # create a vertical "spike line" to compare data across 2 plots
    plotly::layout(
      xaxis = list(
        spikethickness = 1,
        spikedash = "dot",
        spikecolor = "black",
        spikemode = "across+marker",
        spikesnap = "cursor"
      ),
      yaxis = list(spikethickness = 0)
    )
p_combined
```



Save the plot to pull into the index
```{r}
save(p_combined, file = "./all_data.rda")
```


```{r}
rejoin <- readRDS("./rejoin.rds")
```


Build loess smoothing figures figures

```{r}
#create smoothing data frames 
#n1
smooth_n1 <- only_n1 %>% select(-c(Facility)) %>% 
  group_by(date, cases_cum_clarke, new_cases_clarke, X7_day_ave_clarke, cases_per_100000_clarke) %>%
  summarize(sum_copy_num_L = sum(mean_total_copies)) %>%
  ungroup() %>%
  mutate(log_sum_copies_L = log10(sum_copy_num_L)) %>%
  mutate(target = "N1")

#n2
smooth_n2 <- only_n2 %>% select(-c(Facility)) %>% 
  group_by(date, cases_cum_clarke, new_cases_clarke, X7_day_ave_clarke, cases_per_100000_clarke) %>%
  summarize(sum_copy_num_L = sum(mean_total_copies)) %>%
  ungroup() %>%
  mutate(log_sum_copies_L = log10(sum_copy_num_L)) %>%
  mutate(target = "N2")
```


```{r}
#add trendlines 
#extract data from geom_smooth
#average targets extract
# *********************************span 0.6***********************************
#*****************Must always update the n = TOTAL NUMBER OF DAYS*************************
extract <- ggplot(rejoin, aes(x = date, y = log_sum_copies_both)) + 
  stat_smooth(aes(outfit=fit_both<<-..y..), method = "loess", color = '#1B9E77', 
              span = 0.6, n = 240)

#look at the fits to align dates and total observations
#both
extract

#assign fits to a vector
both_trend <- fit_both

#extract y min and max for each
limits_both <- ggplot_build(extract)$data
limits_both <- as.data.frame(limits_both)
both_ymin <- limits_both$ymin
both_ymax <- limits_both$ymax

#reassign dataframes (just to be safe)
work_both <- rejoin

#fill in missing dates to smooth fits
work_both <- work_both %>% complete(date = seq(min(date), max(date), by = "1 day"))
date_vec_both <- work_both$date

#create a new smooth dataframe to layer
smooth_frame_both <- data.frame(date_vec_both, both_trend, both_ymin, both_ymax)

```

```{r}
#make plotlys

#plot smooth frames
p3 <- plotly::plot_ly() %>%
  plotly::add_lines(x = ~date_vec_both, y = ~both_trend,
                    data = smooth_frame_both,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_both,
                                  '</br> Median Log Copies: ', round(both_trend, digits = 2)),
                    line = list(color = '#1B9E77', size = 8, opacity = 0.65),
                    showlegend = FALSE) %>%
plotly::add_ribbons(x ~date_vec_both, ymin = ~both_ymin, ymax = ~both_ymax,
                    showlegend = FALSE,
                    opacity = 0.25,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_both, #leaving in case we want to change
                                  '</br> Max Log Copies: ', round(both_ymax, digits = 2),
                                  '</br> Min Log Copies: ', round(both_ymin, digits = 2)),
                    name = "",
                    fillcolor = '#1B9E77',
                    line = list(color = '#1B9E77')) %>%
                layout(yaxis = list(title = "Total Log SARS CoV-2 Copies", 
                                 showline = TRUE,
                                 automargin = TRUE)) %>%
                layout(xaxis = list(title = "Date")) %>%
    plotly::add_segments(x = as.Date("2020-06-24"), 
                                          xend = as.Date("2020-06-24"), 
                                          y = ~min(both_ymin), yend = ~max(both_ymax),
                                          opacity = 0.35,
                                          name = "Bars Repoen",
                                          hoverinfo = "text",
                                          text = "</br> Bars Reopen",
                                                 "</br> 2020-06-24",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
    plotly::add_segments(x = as.Date("2020-07-09"), 
                                          xend = as.Date("2020-07-09"), 
                                          y = ~min(both_ymin), yend = ~max(both_ymax),
                                          opacity = 0.35,
                                          name = "Mask Mandate",
                                          hoverinfo = "text",
                                          text = "</br> Mask Mandate",
                                                 "</br> 2020-07-09",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
    plotly::add_segments(x = as.Date("2020-08-20"), 
                                          xend = as.Date("2020-08-20"), 
                                          y = ~min(both_ymin), yend = ~max(both_ymax),
                                          opacity = 0.35,
                                          name = "</br> Classes Begin",
                                                 "</br> 2020-08-20",
                                          hoverinfo = "text",
                                          text = "Classes Begin",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
  plotly::add_markers(x = ~date, y = ~log_sum_copies_both,
                      data = rejoin,
                       hoverinfo = "text",
                       showlegend = FALSE,
                       text = ~paste('</br> Date: ', date, 
                                     '</br> Actual Log Copies: ', round(log_sum_copies_both, digits = 2)),
                       marker = list(color = '#1B9E77', size = 6, opacity = 0.65))


p3
```

Create final trend plot by stacking with epidemic curve

```{r}
smooth_extract <-
    plotly::subplot(p3,p1, # plots to combine, top to bottom
      nrows = 2,
      heights = c(.6,.4),  # relative heights of the two plots
      shareX = TRUE,  # plots will share an X axis
      titleY = TRUE
    ) %>%
    # create a vertical "spike line" to compare data across 2 plots
    plotly::layout(
      xaxis = list(
        spikethickness = 1,
        spikedash = "dot",
        spikecolor = "black",
        spikemode = "across+marker",
        spikesnap = "cursor"
      ),
      yaxis = list(spikethickness = 0)
    )

smooth_extract
```



```{r}
save(smooth_extract, file = "./plotly_fig.rda")
```

Save an htmlwidget for website embedding
```{r}
htmlwidgets::saveWidget(smooth_extract, "plotly_fig.html")
```
